---
title: "Reverse Engineering Project"
author: "Hanna Zakharenko"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, [STORY NAME](STORY URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data
library (readr)

urlfile="https://raw.githubusercontent.com/fivethirtyeight/data/master/comic-characters/dc-wikia-data.csv"

dc_characters<-read_csv(url(urlfile))

urlfile2 = "https://raw.githubusercontent.com/fivethirtyeight/data/master/comic-characters/marvel-wikia-data.csv"

marvel_characters<- read_csv((urlfile2))

# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: "Among the characters for which we have gender data, females made up only 29.3 percent of the DC character list and 24.7 percent of the Marvel roster."
* **Analysis summary**: It was hard to determine exactly what result the reporters were saying, so I was unable to find the exact number. I performed analysis comparing females to all genders in the DC character population that there was data for by eliminating the N/A values, as well as comparing females just to data that reported male/female characters, but through both methods I did not get 29.3% (it is 29.14% for male/female and 29.05% for all gender). However, I did get the result from the Marvel roster by using the all sex method, which was 24.7%.

```{r}
#DC CHARACTERS MALE/FEMALE
malefemale_dc_characters <- dc_characters %>%
  filter(!is.na(SEX))%>%
  filter(SEX =="Female Characters" | SEX == "Male Characters")

malefemale_dc_characters %>%
  group_by(SEX) %>%
  summarise(count=n()) %>%
  mutate(percent_of_total = count/6750*100)
```
```{r}
#DC CHARACTERS ALL SEX
allsex_dc_characters <- dc_characters %>%
  filter(!is.na(SEX))

allsex_dc_characters %>%
  group_by(SEX) %>%
  summarise(count=n()) %>%
  mutate(percent_of_total = count/6771*100)
```
```{r}
#MARVEL CHARACTERS ALL SEX
allsex_marvel_characters <- marvel_characters %>%
  filter(!is.na(SEX))

allsex_marvel_characters %>%
  group_by(SEX) %>%
  summarise(count=n()) %>%
  mutate(percent_of_total = count/15522*100)
```
### Sentence 2

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-